Simulation for Correlation Motif

### 2017-09-10 analysis/Simulation.Rmd
wflow_publish("Simulation.Rmd")

---
title: "Simulation for Correlation Motif"
author: "Zhiwei Ma"
date: "8/30/2017"
output:
  html_document:
    toc: false
---
<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=FALSE)
```

>>>>

---
title: "Simulation for Correlation Motif"
author: "Zhiwei Ma"
date: "8/30/2017"
output: html_document
---
<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
